Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-05-22 ms.qmd
Fixed global predcitions figure. Added in new predcitions without posteriprs. NEed to figure out why exactly NA's still excist as they shouldn't

# Now we can merge teh climate datasets together so that we have the species, lat and long, current and future climate. Then we can calculate the expected 'increase' in T into the future

@@

# Now lets merge all_pred with the climate projections
  # Simplify columns 
  climate_data_new <- climate_data  %>% dplyr::select(-Latitude, -Longitude, -Species)

@@

@@

ggsave(p, filename = "./output/figures/fig-preds.png", width = 9.1, height = 7.2)

>>>>

# Now we can merge the climate datasets together so that we have the species, lat and long, current and future climate. Then we can calculate the expected 'increase' in T into the future

@@

# Now lets merge all_pred with the climate projections
  # Simplify columns 
  climate_data_new <- climate_data  %>% dplyr::select(-Latitude, -Longitude)

@@

  all_pred2_no_sum <-  all_pred_no_sum %>% mutate(match = interaction(spp, Latitude, Longitude))  %>% left_join(., climate_data_new, by = "match")

@@

ggsave(p, filename = "./output/figures/fig-preds.png", width = 7.8, height = 10.1)
